Implementing \Kwd{DNS} in \Kwd{C0}

### 2017-12-13 paper.tex
update example code in paper

    if (len >= 0xc0) {
        // case: pointer
        // read the last 14 bits of this word as a
        // pointer into the message (in octets)
        cursor_set(cur, orig_ix + 2);
        int ptr = read_bits(cur, data, 14);

>>>>

    if ((len & 0xc0) == 0xc0) {
        // case: pointer
        // read the remaining bits of this word
        // as a pointer into the message (in octets)
        cursor_set(cur, orig_ix);
        int ptr = c0_ntohs(read_bits(cur, data, 16) & 0xFFFF);
        //@assert ((ptr & 0xc000) == 0xc000);
        ptr &= 0x3fff;
